Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-03 windheat.tex
Fixing "\densSlope"

\subsection{Over Star Formation History}
Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1 \label{eq:MDotSFH}\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1, \label{eq:EDotSFH}
\end{align}
resulting in a wind heating parameter of 
\begin{align}
  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t).
\end{align}
The mass return parameter will be
\begin{align}
\eta = \frac{\dot{M}(t)}{\int_0^t S(t_1) {\rm d}t_1} \th
\end{align}
 % \begin{figure}
 % \includegraphics[width=\columnwidth]{NickPlot2.pdf}
 % \caption{\label{NickPlot2} Effective wind velocities for
 % nonstandard star formation histories.  The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other colors show the effective wind velocities $\mathcal{V}_{\rm w}$ computed using convolved star formation histories $\mathcal{S}(t)$.  The purple curve shows a recent drop in the star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.  Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\epsilon = 0.001$, $\epsilon = 0.1$, and $\epsilon = 0.3$ of their halo-averaged values, respectively. }
 % \end{figure}
We estimate the stellar wind heating provided by the {\it average}
star formation history of galaxies of a given $\Mbh$ using the results
of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
star formation histories in \citet{MosterNaab+:2013a} are in terms of
halo mass. For a given $\Mbh$ we assign the halo mass whose star
formation history would produce a bulge consistent with the
$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A slight complication occurs for the largest mass halos, where much of the $z=0$ stellar mass has been acquired through accretion of satellite halos rather than {\it in situ} star formation.  To accomodate this, we use analytic fits for mass accretion histories $A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, and replace $S(t) \rightarrow S(t)+A(t)$ in Eqs. \ref{eq:MDotSFH} and \ref{eq:EDotSFH}.

>>>>

\subsection{Over Star Formation History}
Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1 \label{eq:MDotSFH}\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1, \label{eq:EDotSFH}
\end{align}
resulting in a wind heating parameter of 
\begin{align}
  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t).
\end{align}
The mass return parameter will be
\begin{align}
\eta = \frac{\dot{M}(t)}{\int_0^t S(t_1) {\rm d}t_1} \th
\end{align}
 \begin{figure}
 \includegraphics[width=\columnwidth]{NickPlot2.pdf}
 \caption{\label{NickPlot2} Effective wind velocities for
 nonstandard star formation histories.  The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other colors show the effective wind velocities $\mathcal{V}_{\rm w}$ computed using convolved star formation histories $\mathcal{S}(t)$.  The purple curve shows a recent drop in the star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.  Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\epsilon = 0.001$, $\epsilon = 0.1$, and $\epsilon = 0.3$ of their halo-averaged values, respectively. }
 \end{figure}
We estimate the stellar wind heating provided by the {\it average}
star formation history of galaxies of a given $\Mbh$ using the results
of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
star formation histories in \citet{MosterNaab+:2013a} are in terms of
halo mass. For a given $\Mbh$ we assign the halo mass whose star
formation history would produce a bulge consistent with the
$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A slight complication occurs for the largest mass halos, where much of the $z=0$ stellar mass has been acquired through accretion of satellite halos rather than {\it in situ} star formation.  To accomodate this, we use analytic fits for mass accretion histories $A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, and replace $S(t) \rightarrow S(t)+A(t)$ in Eqs. \ref{eq:MDotSFH} and \ref{eq:EDotSFH}.
